---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Ryan Wheat"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

This distribution looks negatively skewed. This indicates that students generally give positive course evaluations, creating a bit of ceiling effect. This is what I expected to see: if professors are getting hired at UT Austin, chances are that they're decent at their job. However, just based on probabilities, chances are good that a few of them aren't so great at teaching...

```{r visualize-skew}

ggplot(data = evals, mapping = aes(x = score)) + geom_histogram(color = "grey", fill = "darkorange4") + labs(x = "Course Evaluation Score", y = "Count", title = "Course Evaluation Ratings at UT Austin") + theme_bw()

```


### Exercise 2

```{r score-bty_avg}

ggplot(data = evals, mapping = aes(x = bty_avg, y = score)) + geom_point() + geom_smooth(color = "black")

```


...

Add exercise headings as needed.

## 
For Exercise 12, relevel() function can be helpful! 
