---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Ryan Wheat"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

This distribution looks negatively skewed. This indicates that students generally give positive course evaluations, creating a bit of ceiling effect. This is what I expected to see: if professors are getting hired at UT Austin, chances are that they're decent at their job. However, just based on probabilities, chances are good that a few of them aren't so great at teaching...

```{r visualize-skew}

ggplot(data = evals, mapping = aes(x = score)) + geom_histogram(color = "grey", fill = "darkorange4") + labs(x = "Course Evaluation Score", y = "Count", title = "Course Evaluation Ratings at UT Austin") + theme_bw()

```


### Exercise 2

There seems to be a positive relationship between a professor's beauty and their course evaluation; the more beautiful a lecturer is, the more likely they will receive favorable course evaluations from students.

```{r score-bty_avg}

ggplot(data = evals, mapping = aes(x = bty_avg, y = score)) + geom_point() + geom_smooth(color = "black") + labs(x = "Beauty Rating", y = "Course Evaluation")

cor(evals$bty_avg, evals$score)

```

### Exercise 3

This is a better visualization of the relationship between beauty and evaluation score, because it allows one to see where the data are clustered. In the previous scatterplot, the data look evenly dispersed in a way that does not match the histogram from Exercise 1 (where evaluation scores are clustered around 4), and might make it seem like there is a different distribution of scores than there is. Here, that better matches what we already know and have found.

```{r jitter}

ggplot(data = evals, mapping = aes(x = bty_avg, y = score)) + geom_jitter() + geom_smooth(color = "black") + labs(x = "Beauty Rating", y = "Course Evaluation")

```

### Exercise 4

score = bty_avg(.066) + 3.88

```{r model}

first_model = lm(score ~ bty_avg, data = evals)
summary(first_model)

```

### Exercise 5

```{r with-model-line}

ggplot(data = evals, mapping = aes(x = bty_avg, y = score)) + geom_jitter() + geom_smooth(method = lm, color = "darkorange4", se = FALSE) + labs(x = "Beauty Rating", y = "Course Evaluation")

```

### Exercise 6

Slope Interpretation: a one-unit increase in beauty rating is associated with a .066 unit increase in a professor's course evlauations.

### Exercise 7

Intercept Interpretation: a professor with a beauty rating of 0 would have a course evaluation score of 3.88. In this case, the intercept doesn't make a ton of sense because it's impossible to have a beauty rating of 0. You have to have at least some appearance!

### Exercise 8

R2 = .035

3.5% of the variance in course evaluation scores is explained by a professor's beauty.

### Exercise 9

...

Add exercise headings as needed.

## 
For Exercise 12, relevel() function can be helpful! 
